Viscous Erosion in Porous Media

### 2018-03-29 docs/methods/erosion_methods.tex
NM

@@

We therefore impose the condition of a fixed pressure difference by dynamically controlling the incoming flow-rate, $\umax$. This is achieved by first computing the Stokes flow with $\umax = 1$ prescribed, then measuring the pressure at a location upstream ($x = -2$) and downstream ($x=2$) of the eroding bodies. The vertically-averaged upstream and downstream pressures are given by
\begin{align}
p_{-} = \frac{1}{2} \int_{-1}^{1} p(-2,y) \, dy \, , \qquad
p_{+} = \frac{1}{2} \int_{-1}^{1} p(+2,y) \, dy \, .
\end{align}
We then rescale the computed density function by the pressure difference
\begin{align}
\eeta \leftarrow \frac{\eeta}{(p_{-} - p_{+})} \, .
\end{align}
This rescaling maintains a {\em fixed} pressure difference between the upstream ($x=-2$) and downstream ($x=2$) positions. Because the Stokes equations are linear, such a rescaling is permissible and does not alter the accuracy of our method. Furthermore, {\em dynamic} rescaling is also permissible because the Stokes equations are memoryless (i.e.~there is no time derivative present in the PDEs).

>>>>

We therefore impose the condition of a fixed pressure difference by dynamically controlling the incoming flow-rate, $\umax$. This is achieved by first computing the Stokes flow with $\umax = 1$ prescribed and measuring the pressure at a location upstream ($x = -2$) and downstream ($x=2$) of the eroding bodies. The vertically-averaged upstream and downstream pressures are given by
\begin{align}
p_{-} = \frac{1}{2} \int_{-1}^{1} p(-2,y) \, dy \, , \qquad
p_{+} = \frac{1}{2} \int_{-1}^{1} p(+2,y) \, dy \, .
\end{align}
Next, we rescale the computed density function by the pressure difference
\begin{align}
\eeta \leftarrow \frac{\eeta}{(p_{-} - p_{+})} \, .
\end{align}
This rescaling maintains a {\em fixed} pressure difference between the upstream ($x=-2$) and downstream ($x=2$) positions. Because the Stokes equations are linear, such a rescaling is permissible and does not alter the accuracy of our method. Furthermore, {\em dynamic} rescaling is also permissible because the Stokes equations are memoryless (i.e.~there is no time derivative present in the PDEs).

@@
